Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-11-28 contents/draft.tex
Table 2에 전체 데이터 통계 포함 Table 2를 앞으로 보냄 [Related Work] 섹션을 뒤로 보냄

\documentclass[AMS,STIX2COL]{WileyNJD-v2}

@@

    \begin{center}
        \begin{table*}[t]
            \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
            \centering
            \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
                \toprule
                & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
                alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
                \midrule
                no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
                secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
                tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
                quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
                quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
                \bottomrule
            \end{tabular*}
            \begin{tablenotes}
                \footnotesize
                \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
                \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
            \end{tablenotes}
        \end{table*}
    \end{center}

@@

@@

    The remainder of this paper is organized as follows.
    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
    In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
    In Section ~\ref{sec:re-ranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
    In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.

@@

    \begin{table*}[]
        \caption{Statistics on full data for training and evaluating three morphological analysis models}\label{tab:data-statistics}
        \centering
        \begin{tabular*}{500pt}{@{\extracolsep\fill}|c|c|rrr|rrr|@{\extracolsep\fill}}
            \toprule
            \multicolumn{2}{|c|}{\multirow{2}{*}{\textbf{Corpus}}} & \multicolumn{3}{c|}{\textbf{Training Set}} & \multicolumn{3}{c|}{\textbf{Test Set}} \\
            \cmidrule{3-5} \cmidrule{6-8}
            \multicolumn{2}{|c|}{~} & sentences & eojeols & morphemes & sentences & eojeols & morphemes \\
            \midrule
            \multicolumn{2}{|c|}{Sejong Corpus} & 194,822 & 2,681,582 & 6,033,785 & 49,922 & 678,578 & 1,527,803 \\
            \midrule
            \multirow{3}{*}{UCorpus}         & written     & 4,998,560 & 57,393,332 & 127,171,473 & 53,003 & 598,413 & 1,325,419 \\
            ~                                & semi-spoken & 334,061   & 2,960,146  & 6,468,494   & 38,960 & 332,285 & 726,398   \\
            ~                                & spoken      & 429,215   & 2,295,940  & 5,584,494   & 62,399 & 279,545 & 691,542   \\
            \midrule
            \multirow{2}{*}{Everyone Corpus} & written     & 129,352   & 1,713,367  & 3,944,118   & 14,442 & 191,223 & 440,052   \\
            ~                                & spoken      & 137,869   & 714,021    & 1,440,746   & 19,789 & 85,316  & 170,523   \\
            \bottomrule
        \end{tabular*}
    \end{table*}

>>>>

\documentclass[AMS,STIX2COL]{WileyNJD-v2}
\usepackage{makecell}

@@

    \begin{table*}[]
        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}\label{tab:data-statistics}
        \centering
        \begin{tabular*}{500pt}{@{\extracolsep{\fill}}m{10mm}m{8mm}m{10mm}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{9mm}m{9mm}m{10mm}@{}}
            \toprule
            \multirow{2}{*}{Corpus}                       & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
            \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
            ~                                             & ~                      & Sentences & Eojeols    & Morphs\newline/Sent & Sentences & Eojeols    & Morphs\newline/Sent & Sentences & Eojeols & Morphs\newline/Sent \\
            \midrule
            Sejong\newline Corpus                         & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
            \midrule
            \multirow{3}{*}{UCorpus}                      & written                & 5,456,101 & 62,462,158 & 25.1                & 4,998,560 & 57,393,332 & 25.4                & 53,003    & 598,413 & 25.0                \\
            ~                                             & semi-spoken            & 393,770   & 3,401,444  & 18.4                & 334,061   & 2,960,146  & 19.4                & 38,960    & 332,285 & 18.6                \\
            ~                                             & spoken                 & 627,380   & 2,819,427  & 10.9                & 429,215   & 2,295,940  & 13.0                & 62,399    & 279,545 & 11.1                \\
            \midrule
            \multirow{2}{*}{\makecell{Everyone \\Corpus}} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
            ~                                             & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
            \bottomrule
        \end{tabular*}

    \end{table*}

@@

    \begin{table*}[t]
        \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
        \centering
        \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
            \toprule
            & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
            alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
            \midrule
            no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
            secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
            tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
            quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
            quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
            \bottomrule
        \end{tabular*}
        \begin{tablenotes}
            \footnotesize
            \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
        \end{tablenotes}
    \end{table*}

@@

    The remainder of this paper is organized as follows.
    In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
    In Section ~\ref{sec:re-ranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
    In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.

@@
